---
title: "big data first task"
author: "Ariel & Eitan & Yuval"
date: "2024-07-27"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries
```{r libraries}
library(pacman)
pacman::p_load(
  tidyverse, 
  readr, 
  skimr, 
  knitr,
  dplyr,
  tidyr
)
library(ggplot2)
library(scales)
```

## Load Data
```{r}
listings_data <- read_csv('listings_clean.csv')
calendar_data <- read_csv('calendar_clean.csv')
```


# Part 1 - Descriptive Statistics
```{r}
summary(listings_data)
skim(listings_data)
```
- no missing values for the price_dollars

- המחיר הוא מחיר קטלוג כלומר המחיר שיש בטבלה הזו זה המחיר שבכל הנכס ראה לנכון לרשום לראושנה.
------------------------------------------------------------------

## Single Variable Visualizations
### Plot 1: Distribution of Prices

```{r}
#ggplot(listings_data, aes(x = price_dollars)) +
#  geom_histogram(fill = "blue", color = "black", bins = 50) +
#  labs(title = "Distribution of Nightly Prices", x = "Price (Dollars)", y = "Frequency") +
#  theme_minimal()
```

```{r, echo=TRUE, fig.width=12, fig.height=6}
# Set the number of bins
# num_bins <- 50

# Calculate the bin width
# bin_width <- (max(listings_data$price_dollars, na.rm = TRUE) - min(listings_data$price_dollars, na.rm = TRUE)) / num_bins

# Create the histogram with annotations for the price range
# ggplot(listings_data, aes(x = price_dollars)) +
# geom_histogram(fill = "blue", color = "black", bins = num_bins) +
#  labs(title = "Distribution of Nightly Prices", x = "Price (Dollars)", y = "Frequency") +
#  theme_minimal() +
#  stat_bin(binwidth = bin_width, geom = "text", aes(label = ..count..), vjust = -0.5) +
#  scale_x_continuous(breaks = seq(0, max(listings_data$price_dollars, na.rm = TRUE), bin_width),
#                     labels = scales::dollar_format(prefix = "$", big.mark = ",")) +
#  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r, echo=TRUE, fig.width=14, fig.height=10}
# Create a histogram with 50 bins
hist_data <- hist(listings_data$price_dollars, 
                  breaks = 50, 
                  plot = FALSE)  # Create histogram data without plotting

# Plot the histogram
plot(hist_data, 
     main = "Distribution of Price (Dollars)", 
     xlab = "",
     ylab = "Frequency", 
     col = "blue", 
     border = "black", 
     xaxt = 'n')  # Suppress x-axis labels initially

# Add custom x-axis labels with price ranges
bin_midpoints <- hist_data$mids  # Midpoints of bins
bin_labels <- paste0("[", round(hist_data$breaks[-length(hist_data$breaks)], 2), 
                     ", ", round(hist_data$breaks[-1], 2), ")")  # Bin range labels
axis(1, at = bin_midpoints, labels = bin_labels, las = 2, cex.axis = 0.7)  # Custom x-axis

# Add frequency labels at the top of each bin
text(bin_midpoints, hist_data$counts, labels = hist_data$counts, pos = 3, cex = 0.8)

```
במחשבה שניה אני לא בטוחה עד כמה זה רלוונטי!
לא ממש רואים פה משהו...

אפשר אולי להוסיף כגרף רביעי

* bins = 50 is the number of intervals (bins) into which the data range is divided for the histogram. 
Setting bins = 50 means the entire range of price data is divided into 50 equal intervals.

* X-axis (Price in Dollars): This axis shows the nightly prices of the Airbnb listings. The values range from 0 to over 4000 dollars.

* Y-axis (Frequency): This axis represents the number of listings that fall into each price range (bin).

* Observations - תצפיות: 
* Skewed Distribution (חלוקה מוטה): The plot shows a highly skewed distribution, with most listings clustered at the lower end of the price scale. This indicates that the majority of listings have relatively low nightly rates.

* Outliers: There are a few listings with significantly higher prices, stretching the distribution far to the right. These could be luxury or unique properties that command higher rates.

* Zero or Near-Zero Prices: A spike near the zero price mark might indicate data entry errors or special pricing strategies like promotional offers or placeholders. (שגיאה בנתונים)


* Strategies to Raise Revenue - חיבור לשאלה 4:
TODO

------------------------------------------------------------------

### Plot 2: Distribution of Review Scores
```{r}
#ggplot(listings_data, aes(x = review_scores_rating)) +
#  geom_histogram(fill = "green", color = "black", bins = 10) +
#  labs(title = "Distribution of Review Scores", x = "Review Scores Rating", y = "Frequency") +
#  theme_minimal()
```

```{r, echo=TRUE, fig.width=14, fig.height=10}
# Create a histogram with 10 bins
hist_data <- hist(listings_data$review_scores_rating, 
                  breaks = 10, 
                  plot = FALSE)  # Create histogram data without plotting

# Plot the histogram
plot(hist_data, 
     main = "Distribution of Review Scores", 
     xlab = "Review Scores Rating", 
     ylab = "Frequency", 
     col = "blue", 
     border = "black", 
     xaxt = 'n')  # Suppress x-axis labels initially

# Add custom x-axis labels with price ranges
bin_midpoints <- hist_data$mids  # Midpoints of bins
bin_labels <- paste0("[", round(hist_data$breaks[-length(hist_data$breaks)], 2), 
                     ", ", round(hist_data$breaks[-1], 2), ")")  # Bin range labels
axis(1, at = bin_midpoints, labels = bin_labels, las = 2, cex.axis = 0.7)  # Custom x-axis

# Add frequency labels at the top of each bin
text(bin_midpoints, hist_data$counts, labels = hist_data$counts, pos = 3, cex = 0.8)
```

* Observations - תצפיות: 
* High Concentration of Top Scores: The histogram shows a significant concentration of listings with review scores around 100, indicating that many listings are highly rated by guests. This suggests a generally positive guest experience across many properties. - ריכוז גבוה של ציונים סביב ה100

* Sparse Low Scores: There are very few listings with low review scores, indicating either high satisfaction or that properties with poor ratings are less common or less frequently reviewed. - מעט ציונים נמוכים

* Gap in Middle Scores: There is a noticeable gap in the mid-range scores (25-75), suggesting that listings tend to either be rated very highly or not at all. This could be due to fewer guests leaving reviews or an issue with the scoring system. - רוב הציונים גבוהים ממש או נמוכים

* התוצאות שקיבלנו קצת מוזרות 
איך זה שהרוב 100? מה אין ציונים גרועים? אולי זה קשור לערכים חסרים

```{r}
# Checking the number and percentage of NA (missing) values in the 'review_scores_rating' column
num_na_reviews <- sum(is.na(listings_data$review_scores_rating))
total_reviews <- nrow(listings_data)
percent_na_reviews <- (num_na_reviews / total_reviews) * 100
num_na_reviews
percent_na_reviews
```
Significant percentage of missing values (22.68%)!

Possible Explanations:
הסברים אפשריים לתואה שקיבלנו בגרף:
1. Bias in Review Submissions:
- Happy Guests Are More Likely to Review: Often, guests who have a very positive experience are more motivated to leave reviews, especially if they feel strongly about their experience. This can lead to a skew in the data where high scores dominate.
- Cultural or Platform Bias: In some cultures or platforms, there might be a tendency to avoid leaving negative feedback unless the experience was extremely poor. This cultural bias can result in predominantly high ratings.

2. Selection Bias:
- Listing Curation: Airbnb hosts might selectively encourage satisfied guests to leave reviews, while not prompting those who might leave lower scores. 
נעודד רק את אלו שנהנו להשאיר ציון
- ncentives for Positive Reviews: Sometimes, hosts offer incentives for positive reviews, intentionally or not, which can skew the distribution towards higher scores.
תמריצים להשארת ציון גבוה

3. Missing Data Impact:
- Non-Reviewed Stays: The missing review data (22.68%) could represent stays that were either not reviewed by guests or the reviews were withheld. These missing reviews could potentially include more negative experiences.
- Systematic Omission: If the missing data disproportionately represents lower scores, this would skew the visible data towards higher scores. It’s essential to understand why these values are missing—whether due to guest inaction, system errors, or intentional omission.
האם הערכים החסרים מעידים על ציונים נמוכים?
אולי זה לא מושכר ולכן יש ערכים חסרים ואין לזה ציון!

* Strategies to Raise Revenue - חיבור לשאלה 4:
רוב הציונים אכן גבוהים, יכול להראות קצת חשוד כי יכול להיות שיש פה רמאות כלשהי(גם אם לא במכוון)
על כן נעדיף להסתכל על זה בעין חשדנית
נרצה לבדוק יותר מאוחר את הקשר למחיר ואת הקשר להזמנות שבוצעו בפועל.


------------------------------------------------------------------
### Plot 3: Distribution of the number of beds
```{r}
ggplot(listings_data, aes(x = factor(beds))) +
  geom_bar(fill = "purple", color = "black") +
  labs(title = "Distribution of Number of Beds in Listings", x = "Number of Beds", y = "Frequency") +
  theme_minimal()
```

למה בחרנו בזה?:
- Variable Choice: Number of Beds - The number of beds in a listing is crucial as it determines the accommodation capacity, influencing both pricing and the target market. Listings with more beds can attract larger groups, such as families or group travelers, potentially leading to higher per-night revenue. This variable also allows targeting different market segments, which can significantly affect booking rates and pricing strategies.
מדובר בפרמטר קריטי שקובע את קיבולת האירוח ועל מס' הלנים.

ניתן לראות שרוב הדיור שמושכר הוא עם מיטה אחת-2, זה יכול להיות מעט בעייתי בעיקר אם רוצים להגדיל הכנסות.
דיור בעל מספר גדול יותר של מיטות יהיה מושכר בעלות יותר גדולה מאחר ויש קשר בין גודל הנכס למספר המיות בו, 
הגיוני שנכנס גדול יותר יכיל יותר מיטות ולכן יהיה מושכר ביותר כסף.
הייתי ממליצה להציע יותר נכסים בעלי מספר גדול יותר של מיטות (זה גם מכניס יותר כסף וגם מגדיל את מגוון ההיצע שיש לאירביאנדבי להציע)


------------------------------------------------------------------
### Plot 4: Distribution of Host Response Times

```{r, echo=TRUE, fig.width=14, fig.height=8}
# Count the occurrences of each response category
response_counts <- table(listings_data$host_response_time)

# Set up the plotting area with more space for axis labels
par(mar = c(7, 4, 4, 2) + 0.1)  # Adjust bottom margin to provide more space

# Plot the bar chart with adjusted y-axis limit
bp <- barplot(response_counts,
              main = "Distribution of Host Response Times",
              ylab = "Frequency",
              col = "lightblue",
              las = 1,  # Make the labels horizontal
              cex.names = 1.2,  # Increase the size of the axis labels
              ylim = c(0, 1500))  # Set y-axis limit up to 1400

# Add frequency labels above each bar
text(x = bp, y = response_counts, labels = response_counts, pos = 3, cex = 1.0, col = "black")

# Reset margins to default
par(mar = c(5, 4, 4, 2) + 0.1)

```
לא אומר הרבה....
זה תוצאות טובות שהרוב עונים מהר
כנראה ימחק!

------------------------------------------------------------------
### Plot 5: Distribution of property Type
```{r, echo=TRUE, fig.width=14, fig.height=8}
# Count the occurrences of each property type
response_counts <- table(listings_data$property_type)

# Set up the plotting area with more space for axis labels
par(mar = c(12, 4, 4, 2) + 0.1)  # Increase bottom margin for rotated labels

# Plot the bar chart with adjusted y-axis limit
bp <- barplot(response_counts,
              main = "Distribution of Property Types",
              ylab = "Frequency",
              col = "lightblue",
              las = 2,  # Rotate the labels to be perpendicular to the axis
              cex.names = 0.8,  # Adjust size of axis labels
              ylim = c(0, 3000))  # Set y-axis limit

# Add frequency labels above each bar
text(x = bp, y = response_counts, labels = response_counts, pos = 3, cex = 0.8, col = "black")

# Reset margins to default
par(mar = c(5, 4, 4, 2) + 0.1)

```

חסר מגוון!
אולי הגדלת המגוון עשויה להביא סוג נוסף של לקוחות שמעוניין להשכיר דיור אחר ולא רק דירות ובכך להגדיל את הרווחים.

The graph shows a predominance of apartments (2,612 listings) among available rental properties, with other types like houses (562 listings) being far less common. This indicates a lack of variety in accommodations. To attract a broader customer base, the platform should encourage more listings of diverse property types, such as boats, camper/RVs, and villas. Increasing variety can appeal to niche markets and potentially boost bookings. Diversifying property offerings could lead to increased profits by catering to different traveler preferences.

* Strategies to Raise Revenue - חיבור לשאלה 4:
נמליץ באופן כללי להציע מגוון רחב יותר של נכסים על מנת להגיע ליותר סוגי אנשים ולעלות על צרכיהם.

------------------------------------------------------------------

## Multi-Variable Analysis
### Plot 1: Average Review Scores by Neighbourhood with Listing Count

```{r, echo=TRUE, fig.width=14, fig.height=8}

# Filter out rows with missing review_scores_location or num_listings
neighborhood_data <- listings_data %>%
  group_by(neighbourhood) %>%
  summarise(
    avg_review_score = mean(review_scores_location, na.rm = TRUE),
    num_listings = n()
  ) %>%
  filter(!is.na(avg_review_score) & !is.na(num_listings))

# Plot 1: Average Review Scores by Neighbourhood with Listing Count
ggplot(neighborhood_data, aes(x = reorder(neighbourhood, -avg_review_score), y = avg_review_score, size = num_listings)) +
  geom_point(alpha = 0.6, color = "blue") +
  scale_size_area(max_size = 20) +
  labs(title = "Average Review Scores by Neighbourhood with Listing Count",
       x = "Neighbourhood",
       y = "Average Review Score (Location)",
       size = "Number of Listings") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
    plot.title = element_text(hjust = 0.5)
  )

```

The bubble plot shows the relationship between average review scores for location and the number of listings across different neighborhoods. Notably, neighborhoods like Brookline and Chestnut Hill have high average review scores, suggesting they are well-regarded by guests for their location. However, these areas also have fewer listings, indicating potential for growth. On the other hand, neighborhoods like Allston-Brighton and Back Bay have a high number of listings but comparatively lower average review scores, suggesting these areas are popular but might benefit from improvements in location-related amenities.

Recommendation: To maximize profitability and guest satisfaction, consider investing in increasing the number of listings in high-scoring neighborhoods, as these areas are already preferred by guests for their location. Additionally, improving amenities and services in lower-scoring but popular neighborhoods could enhance guest experiences, potentially leading to higher ratings and increased bookings. This balanced approach could optimize both guest satisfaction and revenue growth.

אזורים שנחשבים לטובים עדיף להשכיר בהם יותר!

------------------------------------------------------------------

### Plot 2: Relationship Between Review Scores and Prices by Number of Beds

```{r, echo=TRUE, fig.width=14, fig.height=8}
# Filter out missing values
#data_filtered <- listings_data %>%
#  filter(!is.na(price_dollars) & !is.na(review_scores_rating) & !is.na(beds))

# Scatter Plot with Facets by Number of Beds
#ggplot(data_filtered, aes(x = review_scores_rating, y = price_dollars)) +
#  geom_point(alpha = 0.6, color = "blue") +
#  facet_wrap(~ beds, scales = "free_y", ncol = 3) +
#  labs(title = "Review Scores vs Price by Number of Beds",
#       x = "Review Scores Rating",
#       y = "Price (Dollars)") +
#  theme_minimal() +
#  theme(strip.text = element_text(size = 10),
#        plot.title = element_text(hjust = 0.5))
```

הסבר:
- Review Scores on the X-axis: Displays how guest ratings relate to pricing.
- Price on the Y-axis: Shows the variation in prices for listings with different review scores.
- Facets for Number of Beds: Each facet represents a different bed category, helping to see patterns or trends specific to each category.

הגרף הזה לא ממש עוזר לי להבין משהו - כנראה ימחק! 


------------------------------------------------------------------

### Plot 3: Correlation of Various Review Aspects with Overall Review Score

```{r}
# Calculate correlation coefficients
correlations <- listings_data %>%
  select(review_scores_rating, review_scores_communication, review_scores_checkin, review_scores_cleanliness, review_scores_accuracy) %>%
  summarise(across(starts_with("review_scores"), ~cor(review_scores_rating, ., use = "complete.obs"))) %>%
  pivot_longer(cols = -review_scores_rating, names_to = "Aspect", values_to = "Correlation")

# Plot the correlations
ggplot(correlations, aes(x = reorder(Aspect, Correlation), y = Correlation, fill = Aspect)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Correlation of Various Review Aspects with Overall Review Score Rating", 
       x = "Review Aspect", 
       y = "Correlation Coefficient") +
  theme_minimal() +
  scale_fill_brewer(palette = "Blues")
```
תובנות:
The bar plot above illustrates the correlation between various review aspects (cleanliness, accuracy, communication, and check-in) and the overall review score rating for Airbnb listings. 
The higher the correlation coefficient, the stronger the relationship between the aspect and the overall rating.
In this case, "cleanliness" has the highest correlation with the overall review score, followed by "accuracy," "communication," and "check-in." 
This suggests that guests value cleanliness the most when rating their stay, indicating that hosts should prioritize maintaining a clean environment.
Additionally, focusing on accuracy in listings, effective communication, and a smooth check-in process can also enhance guest satisfaction and lead to higher ratings.
Therefore, hosts are recommended to pay particular attention to cleanliness, as it significantly influences guest perceptions and overall satisfaction.

ניקיון משפיע הכי הרבה כדאי למארח לשים לב לזה, זה יעלה את הציון שלו ועשוי להביא לו יותר לקוחות ובכך להעלות רווחים.

------------------------------------------------------------------

### Graph 4: Average Price by Review Score Bands and Number of Beds

```{r}

# Define bins for review scores
bins <- cut(listings_data$review_scores_rating, breaks = seq(0, 100, by = 20), include.lowest = TRUE)

# Add bins to the data
listings_data$score_bins <- bins

# Calculate average price for each bin and number of beds
average_price_by_bin_beds <- aggregate(price_dollars ~ score_bins + beds, data = listings_data, FUN = mean, na.rm = TRUE)

# Plot the average price by review score bins and number of beds
ggplot(average_price_by_bin_beds, aes(x = score_bins, y = price_dollars, fill = as.factor(beds))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Average Price by Review Score Bands and Number of Beds", x = "Review Score Bands", y = "Average Price (Dollars)", fill = "Number of Beds") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```

הסבר - מה רואים:
This graph displays the average price of Airbnb listings across different review score bands, segmented by the number of beds.
The x-axis represents review score bands, while the y-axis shows the average price in dollars. 
Different colors indicate the number of beds in each listing.
הצגנו את הציונים השונים תוך קיבוץ לקבוצות ואת המחיר שנדרש עבור כל קבוצת ציון, כאשר חילקנו למספר חדרים - זאת על מנת לנקות את השפעת גודל הנכס.

תובנות:
From the graph, it is evident that the relationship between review scores and price varies by the number of beds. 
Listings with one bed show less variation in price across different review score bands, suggesting that review scores may not significantly impact pricing for these smaller units. 
In contrast, listings with more beds, particularly those in higher review score bands (60-100), generally command higher prices. 
This trend implies that larger listings with better reviews can justify higher prices.

המלצה:
Property owners, especially those with multiple beds, should focus on improving their review scores to enhance their value perception. 
By investing in the quality and amenities of their properties, they can achieve higher ratings, which in turn can justify higher nightly rates and increase overall profitability.

נמליץ לבעלי הנכסים עם ציונים גבוהים להעלות את המחיר לנכס שלהם - הם יכולים לעשות זאת כי השקעה שווה כסף.


------------------------------------------------------------------


# Part 2 - Business Metrics

## Merge the CSVs
```{r}
# Rename price_dollars to org_price in listings_data
listings_data_copy <- listings_data %>% rename(org_price = price_dollars)

# Create copy
calendar_data_copy <- calendar_data
```

```{r}
# Merge the dataframes on listing_id
merged_data <- merge(
  calendar_data,
  listings_data_copy,
  by.x = "listing_id",
  by.y = "id"
)
```

*** available_category חידוד בנוגע למשתנה :
- available_category = 0: הנכס הוצע על ידי המארח אבל לא הוזמן ע"י לקוח
- available_category = 1: הנכס הוצע על ידי המארח והוזמן ע"י לקוח
- תאריך שלא הופיע זה תאריך שלא הוצע ע" המארח

## 1. Growth

הגדרת המטריקה:
מטריקה המראה את ההכנסה ההמוצעת ללילה (תאריך) זמין עך ידי המארח עבור כל נכס.
הוא מספק תובנות לגבי האפקטיביות של אסטרטגיית התמחור של הנכס וביצועי ההכנסות הכוללים שלו.

* RevPAN measures the average revenue generated per night that a listing is available for booking, calculated monthly. It combines the effects of pricing strategies (Average Daily Rate, ADR) and booking success (Occupancy Rate), offering a comprehensive view of how effectively a listing utilizes its availability to generate income.

* RevPAN per listing assesses the revenue efficiency by indicating the revenue generated per available night on average. This metric is crucial for understanding the balance between setting competitive prices and achieving high occupancy rates, enabling property managers and hosts to optimize their strategies to maximize income.

Also read here:
- https://airbtics.com/revpan/ -> הכי מדוייק לנו
- https://help.usewheelhouse.com/en/articles/1817194-understanding-the-revenue-per-available-night-chart
- https://www.lake.com/help/glossary/revenue-per-available-night/
- https://roompricegenie.com/revpar-what-is-revpar/
- https://lodgable.com/airbnb-kpis/
- https://hostify.com/blog/key-airbnb-performance-metrics-hosts-should-track
- https://www.airdna.co/blog/vacation-rental-metrics-revpar

* The formula:

  1. RevPAN = ADR × Occupancy Rate per month

  Where:
  - ADR (Average Daily Rate) = Total listing Revenue / # Nights Booked
  - Occupancy Rate = # Nights Booked / # All Nights per listing
  
  ** # Nights Booked = # nights where the listing was rented out, 
  where available_category = 1
  
  ** Total Listing Revenue = sum of price_dollars for a listing where available_category = 1 (indicating the room was available and booked).
  
  ** # All Nights per Listing = both booked and unbooked nights within the month.
  
  ** Average Daily Rate (ADR): This is how much a host charges per day for their rental,
  reflecting the pricing strategy of the property.
  
  ** Occupancy Rates: This metric shows the percentage of available rooms or rentals occupied at a given time. 
  It helps property managers understand the demand and attractiveness of their property.
  
  or
  
  2. RevPAN = Total listing Revenue / # All Nights per listing  
  
  This formula directly calculates RevPAN by dividing the total revenue by the total number of available nights for the listing in a given month.

* רוב הנכסים עם מספר זהה יחסית של לילות (המכנה) ->חשוב להראות את זה

* אפשר לחשוב על מדד זה כעל פוטנציאל רווח עבור כל נכס:
  - איך נתרגם מטריקה זו לצמיחה?
  עבור הנכסים עם פוטנציאל נמוך נצטרך לחשוב או לבנות אסטרטגיה לצורך העלאת הרווח.
  
  1. עבור תפוסה נמוכה - נוריד מחיר 
    נרצה להעלות את פוטנציאל הנכס, 
    הרי התפוסה שלו נמוכה אז כנראה בעל הנכס מבקש עבורו מחיר גבוה מידיי. 
    נמליץ לו להוריד מעט את המחיר על מנת למשוך יותר לקוחות.
    
  2. עבור תפוסה מלאה - נעלה מחיר 
    נרצה להעלות את פוטנציאל הנכס,
    הרי התפוסה מלאה כלומר אנשים אוהבים את הנכס אבל אין פוטנציאל הרווח שלו לא ממומש.
    נמליץ לבעל הנכס להעלות את המחיר וכך ירוויח יותר.
    
*  חשוב- כאן נעשה את המדד עבור כל חודש של ליסטינג, כל נכס מקבל ציון מהמדד עבור כל חודש.


מה היא תופסת ומה מפספסת:

* Includes:
  1. 
  
  
  

מדד:

### 1. RevPAN Using ADR and Occupancy Rate
```{r}
# Ensure data is properly formatted
merged_data$price_dollars <- as.numeric(gsub("[\\$,]", "", merged_data$price_dollars))
merged_data$date <- as.Date(merged_data$date, format="%m/%d/%Y")

# Extract year-month for grouping
merged_data <- merged_data %>%
  mutate(year_month = format(date, "%Y-%m"))

```

```{r}
# Calculate RevPAN per listing per month
revpan_data <- merged_data %>%
  filter(!is.na(price_dollars) & available_category == 1) %>%
  group_by(listing_id, year_month) %>%
  summarise(
    total_revenue = sum(price_dollars, na.rm = TRUE),
    nights_booked = n(),
    total_nights = n_distinct(date),
    ADR = total_revenue / nights_booked,
    occupancy_rate = nights_booked / total_nights,
    RevPAN = total_revenue / total_nights,
    .groups = "drop"
  )
```


```{r}
# Display the results
revpan_data
```

```{r}
# Sample 5 random listings
set.seed(123)  # For reproducibility
random_listings <- sample(unique(revpan_data$listing_id), 5)
random_listings
```


```{r}
# Filter data for these listings
plot_data <- revpan_data %>% filter(listing_id %in% random_listings)

# Plot
ggplot(plot_data, aes(x = year_month, y = RevPAN, group = listing_id, color = factor(listing_id))) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  labs(title = "RevPAN Over Time for Random Listings",
       x = "Month",
       y = "RevPAN (Revenue per Available Night)",
       color = "Listing ID") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
# Summarize RevPAN data by month
revpan_summary <- revpan_data %>%
  group_by(year_month) %>%
  summarise(avg_revpan = mean(RevPAN, na.rm = TRUE))

# Plot RevPAN over time
ggplot(revpan_summary, aes(x = year_month, y = avg_revpan)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "red", size = 2) +
  labs(title = "Monthly RevPAN Trend",
       x = "Month",
       y = "Average RevPAN (Revenue per Available Night)",
       caption = "Source: Airbnb Data") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
- This is a visual representation of the RevPAN (Revenue per Available Night) over time, averaged across all listings.
- This visualization helps in identifying trends, seasonal patterns, and potential impacts of external factors on revenue efficiency.


דעה:
TODO

------------------------------------------------------------------

## 2. Growth by Neighborhood

הגדרת המטריקה:
TODO

* Refers to analyzing and measuring the performance and development of Airbnb properties in different neighborhoods over time.

* Neighborhood RevPAN -  Measure RevPAN specifically for each neighborhood to understand which areas generate the most revenue per available room.

* The formula:

  Neighborhood RevPAN = Neighborhood ADR × Neighborhood Occupancy Rate
  
  Where:

  Neighborhood ADR (Average Daily Rate) = 
  Total listing Revenue per Neighborhood / 
  # Nights Booked in Neighborhood
   
  Neighborhood Occupancy Rate = 
  # Nights Booked in Neighborhood /
  # All Nights per Neighborhood
 
  Or
  
  Neighborhood RevPAN = Total Listing Revenue per Neighborhood / # All Nights per Neighborhood

* כאן נרצה לעשות מרג בין הטבלאות ולהסתכל על הנכסים של כל שכונה.
  נחשב את הרווח של כל שכונה ונחלק במספר הלילות הרלוונטיות בלבד (כאלה שיש עבורן מחיר.)
  כל שכונה תקבל ציון.
  
* כאן נסתכל על פוטנציאל הרווח של השכונות.

* אפשר להסתכל על אחוז הלילות בהן הנכס הוצע להשכרה:
  מספר התאריכים שמופיעים בטבלה / ההפרש בין התאריך הכי גבוה לתאריך הכי נכון
  (נבדוק אם זה אומר לנו משהו?)

מה היא תופסת ומה מפספסת:
TODO

מדד:
```{r}
#TODO
```

דעה:
TODO


------------------------------------------------------------------


## 3. Price Change

הגדרת המטריקה:
TODO

* הנחה: מה ששולם בפועל עבור כל ליסטיל זה כמות הכסף שבעל הנכס ביקש לילה בפועל

* חישוב שונות במחיר על ידי הפרשי דלתות

* Refers to analyzing the variation between the original listed price of Airbnb properties (org_price) and the actual prices paid (price_dollars) over time. 

* Average Price Deviation - Measures the average difference between the original listed price and the actual price paid for all bookings.

* The formula:

  Average Price Deviation = sum(price_dollars - org_price) / # of booking
  
* Average Price Deviation provides valuable insights into the effectiveness of pricing strategies and the dynamics of market demand.  
  
* כאן נוכל להבין האם בעל הנכס הצליח להשכיר יותר ממה שחשב בהתחלה או פחות:

 - Positive Deviation: If price_dollars frequently exceeds org_price, it suggests strong demand, allowing for higher prices than initially expected. This could indicate that the listing is undervalued, presenting an opportunity to increase the original listing price.
 
 - Negative Deviation: Conversely, if price_dollars is often lower than org_price, it may suggest overpricing or a need to discount to attract bookings, indicating a potential issue with demand at the original price point.
 
* Market Sensitivity and Flexibility:
The metric reveals how sensitive the market is to price changes and how flexible the pricing strategy needs to be. Regular adjustments may reflect seasonal trends, special events, or competitive pressures.

* Revenue Optimization:
Understanding the average deviation helps in optimizing revenue management strategies. For instance, consistently lower actual prices might indicate a need for dynamic pricing strategies or better market analysis to set more competitive prices initially.



מה היא תופסת ומה מפספסת:
TODO

מדד:
```{r}
#TODO
```

דעה:
TODO


------------------------------------------------------------------




# Part 3 - Outliers

The first part is to identify a period of time in which the behavior is abnormal.

מה שאפשר לעשות זה גרף עם אחוזי תפוסה לכל יום:
ציר האיקס - ימים
ציר הווי - אחוזי תפוסה פר תאריך

לאחר מכן, נוכל להבין אם יש טווחי זמן שהם מוזרים: אחוזי תפוסה גבוהים או נמוכים מהרגיל ולפי זה נדע להתמקד על התקופת זמן ולהבין מה קורה שם, אולי זאת תקופת חגים.

```{r}
#TODO
```

-----------------------------------


The second part is clearing outliers for:
1. Beds
2. Price

נזכור שקודם נרצה לטפל בערכים החסרים!

```{r}
#TODO
```